\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\date{}

\begin{document}

\textbf{African Leadership University}

Artificial Intelligence group work

7th March 2021

\textbf{Facilitator Name:}

Kudakwashe Dandajena

\textbf{Group Members}

\begin{itemize}
\item
  \begin{quote}
  Agnes Fusese
  \end{quote}
\item
  \begin{quote}
  Ahmed Ramadan Abdelsame Meshref
  \end{quote}
\item
  \begin{quote}
  Doreen Lawuratu Baidoo
  \end{quote}
\item
  \begin{quote}
  Comfort Sibanda
  \end{quote}
\item
  \begin{quote}
  Paul Arah
  \end{quote}
\end{itemize}

\textbf{Client Company}: \href{https://www.rra.gov.rw/}{Rwanda Revenue
Authority}

\textbf{Client Email:} info@rra.gov.rw

\textbf{Client Address:} KG 1 Roundabout, Kigali

\begin{quote}
\textbf{Table of Contents}
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \begin{quote}
  Introduction
  \end{quote}
\item
  \begin{quote}
  Background
  \end{quote}
\item
  \begin{quote}
  Environment
  \end{quote}
\item
  \begin{quote}
  Requirements
  \end{quote}
\item
  \begin{quote}
  Team members contribution
  \end{quote}
\item
  \begin{quote}
  Conclusion
  \end{quote}
\end{enumerate}

\begin{quote}
\textbf{Introduction}
\end{quote}

This project aims to understand the commercial performance of Netflix in
the last five years. This is achieved by performing exploratory data
analysis on Kaggle's updated Netflix data and exploring viable metrics
like shows trends, countries with the most movie production, etc.

\begin{quote}
\textbf{Background}
\end{quote}

Netflix, Inc. is an American over-the-top content platform and
production company headquartered in Los Gatos, California. Netflix was
founded in 1997 by Reed Hastings and Marc Randolph in Scotts Valley,
California. Netflix is a streaming service that offers a wide variety of
award-winning TV shows, movies, anime, documentaries, and more on
thousands of internet-connected devices. (Netflix, 2021).

\begin{quote}
\textbf{Environment Needed to Scale }
\end{quote}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  \begin{quote}
  A server with a publicly available IP address. Popular OS like Linux,
  Windows, macOS, and FreeBSD
  \end{quote}
\item
  \begin{quote}
  A working Python or Anaconda installation bundled with a not less than
  python 3.2 version.
  \end{quote}
\item
  \begin{quote}
  Installation via the respective package managers(pip, conda, etc) of
  the required libraries and dependencies.
  \end{quote}
\item
  \begin{quote}
  Working installation of Jupyter notebook.
  \end{quote}
\end{enumerate}

\textbf{Implementation Timelines}

This project is estimated to take a duration of 3 weeks. The first week
is spent collaborating with all the relevant stakeholders, understanding
the business context, defining the project scope and sourcing the right
data. The second week will be spent cleaning and analysing the data. And
the final week will be spent drawing conclusions and communicating these
back to the relevant stakeholders.

\textbf{Risk}

\begin{itemize}
\item
  \begin{quote}
  Inadequate data: This might affect the quality of the analysis
  \end{quote}
\end{itemize}

\textbf{Requirements}

\begin{itemize}
\item
  \begin{quote}
  Data source
  \end{quote}
\item
  \begin{quote}
  Human resources(data scientist, data analyst, data engineers, software
  developers, DevOps engineers, etc)
  \end{quote}
\item
  \begin{quote}
  Material resources(servers, work pc, GPUs, etc).
  \end{quote}
\end{itemize}

\textbf{Requirements}

\begin{itemize}
\item
  \begin{quote}
  Data Analysis and Jupyter Notebook - Ahmed Meshef
  \end{quote}
\item
  \begin{quote}
  Documentation - Paul Arah
  \end{quote}
\item
  \begin{quote}
  Presentation - Paul Arah and Ahmed Meshef
  \end{quote}
\item
  \begin{quote}
  Research Paul Arah and Ahmed Meshref.
  \end{quote}
\end{itemize}

\textbf{Conclusion}

\begin{quote}
A detailed description of our entire data analysis workflow and
conclusions documented in the slides and Jupyter notebooks.
\end{quote}

\textbf{References}:

\begin{itemize}
\item
  \begin{quote}
  {[}1{]}"Netflix Movies and TV Shows", Kaggle.com, 2021. {[}Online{]}.
  Available: https://www.kaggle.com/shivamb/netflix-shows. {[}Accessed:
  07- Mar- 2021{]}.
  \end{quote}
\end{itemize}

\end{document}
